### 2022-10-18 chapters/conclusion.tex
add : extra figures for greenfaas

First, we will consider taking advantage of the popularity of CI/CD among developers to provide some insights into the energy consumption of their code.
We did prototype a sonar tool that can report on the energy consumption of Java-based code repository.
Figure~\ref{fig:JunitSonarplugin} shows the work of our intern who used a Sonar plugin to highlight the energy evolution of Java applications along time.
This prototype got even more sophisticated to become Joule-dff\link{https://github.com/davidson-consulting/diff-jjoules}, which is a tool to be added in a continuous integration to highlight the energy evolution of the Java programs.
We intend to push this even further to detect the commits responsible for an increase or the optimization within the source code.

@@

\begin{enumerate}

>>>>

First, we will consider taking advantage of the popularity of CI/CD among developers to provide some insights into the energy consumption of their code.
We did prototype a sonar tool that can report on the energy consumption of Java-based code repository.
Figure~\ref{fig:JunitSonarplugin} shows the work of our intern who used a Sonar plugin to highlight the energy evolution of Java applications along time.
This prototype got even more sophisticated to become Joule-dff\link{https://github.com/davidson-consulting/diff-jjoules}, which is a tool to be added in continuous integration to highlight the energy evolution of the Java programs.
We intend to push this even further to detect the commits responsible for an increase or the optimization within the source code.

@@

\begin{figure}[!h]
      \centering
      \caption{Evolution of CPU power}
      \label{fig:power_evolution_greenfaas}
      \includegraphics[width=\linewidth]{chapters/power_evolution_greenfaas}

\end{figure}

\begin{figure}[!h]
      \centering
      \caption{Evolution of CPU behavior during multiple contexts }
      \label{fig:green_faas}
      \includegraphics[width=\linewidth]{chapters/green_faas_duration}
      \includegraphics[width=\linewidth]{chapters/green_faas_energy}
      \includegraphics[width=\linewidth]{chapters/green_faas_power}
      \includegraphics[width=\linewidth]{chapters/green_faas_impact}
      \includegraphics[width=\linewidth]{chapters/soa_energy_efficiency}

\end{figure}

exp graph coloration benchmark
\url{https://github.com/chakib-belgaid/lazy-green-code-test}

setup
Intel(R) Core(TM) i7-3740QM CPU @ 2.70GHz
8 cores 16 GB RAM
\begin{enumerate}
